\profile%[pictures/Taketa]
{Naoto Taketa}{received the B.S. and M.S. degrees in Information Sciences from Hiroshima City University, in 2022 and 2024, respectively.
He is currently with Rakuten Card Co., Ltd., System Strategy Department, System Division.}

\profile%[pictures/uchida]
{Tomoyuki Uchida}{ received the B.S. degree in Mathematics and the M.S. 
and Dr. Sci. degrees in Information Systems from Kyushu
University in 1989, 1991 and 1994, respectively. 
He is currently a professor in the Graduate School of Information Sciences, Hiroshima City University, Hiroshima, Japan. 
His research interests include data mining from graph-structured data,
algorithmic graph theory, graph grammar, and computational learning theory.
}

\profile%[pictures/shoudai]
{Takayoshi Shoudai}{ received the B.S. and M.S. degrees
in Mathematics in 1986 and 1988, respectively, and the Dr. Sci. degree in 1993 in Information Science from Kyushu University. 
He is currently a professor in the
Department of Computer Science and Engineering, Fukuoka Institute of Technology, Fukuoka, Japan.
His research interests include graph algorithms, computational learning theory and machine learning.
}

\profile%[pictures/matumoto]
{Satoshi Matsumoto}{received the B.S. degree in Mathematics, the M.S. and Dr. Sci. degrees in Information Systems from Kyushu University in 1993, 1995 and 1998, respectively.
He is currently a professor in the Department of Mathematical Sciences,
Tokai University, Kanagawa, Japan.
His research interests include computational learning theory and machine learning.}

\profile%[pictures/suzuki]
{Yusuke Suzuki}{ received the B.S. degree in Physics, 
the M.S. and Dr. Sci. degrees in Informatics from
Kyushu University in 2000, 2002 and 2007, respectively.
He is currently a lecturer in the
Graduate School of Information Sciences, Hiroshima City University, Hiroshima, Japan.
His research interests include graph algorithms, machine learning and data mining from graph-structured data.}

\profile%[pictures/miyahara]
{Tetsuhiro Miyahara}{ received the B.S. degree in Mathematics and the M.S. and Dr. Sci. degrees in Information Systems from Kyushu University in 1984, 
1986 and 1996, respectively. 
He is currently an associate professor in the Graduate School of Information Sciences, 
Hiroshima City University, Hiroshima, Japan. 
His research interests include computational learning theory, knowledge 
discovery and machine learning.}

